### 2021-09-14 sections/healthcare_application/main.tex
Add more around analysing games
- Include short Nash equilibrium paragraph and why we will not use it
- Include small numeric example of NE
- Include mathematics around asymmetric replicator dynamics

In order to analyse the strategies played by the two EDs, the learning algorithm
asymmetric replicator dynamics is used \cite{asymmetricreplicatordynamics}.
The use of a learning algorithm allows to investigate, not only the outcome of 
the game, but also how that outcome is reached.
Consider figure \ref{fig:ard-by-itself}. 
By running asymmetric replicator dynamics on the system the behaviour that 
emerges can be observed.
It can be seen that for this particular set of parameters the strategies of 
the two hospitals converge over time. 
Both hospital 1 (row player) and hospital 2 (column player) seem to be playing 
the same strategy \(s_10\) which indicates that thresholds \(T_1 = 10\) and 
\(T_2 = 10\) are played.
What is more important in this example is how the two hospitals reached these
decisions which also highlights the importance of using a learning algorithm.
Hospital 2 is able to reach the decision in a short amount of time while 
hospital 1 takes longer and goes through numerous strategies to get there.

@@

\begin{multicols}{3}
    \begin{itemize}
        \item \( \lambda_{1_1} \) = 1
        \item \( \mu_1 \) = 2
        \item \( C_1 \) = 2
        \item \( N_1 \) = 10
        \item \( M_1 \) = 6

        \columnbreak
        \item \( \lambda_{1_2} \) = 2
        \item \( \mu_2 \) = 2.5
        \item \( C_2 \) = 2
        \item \( N_2 \) = 10
        \item \( M_2 \) = 6

        \columnbreak
        \item \( \lambda_2 \) = 2
        \item \( R \) = 2
        \item \( \alpha \) = 0.5
    \end{itemize}
\end{multicols}

>>>>

The most commonly used method for analysing normal form games is the Nash 
equilibrium \cite{kreps1989nash}. 
The Nash equilibrium is the point of the game were players have no incentive to 
deviate from their strategy.
Consider the following game:

\begin{multicols}{3}
    \begin{itemize}
        \item \( \lambda_{1_1} \) = 1
        \item \( \mu_1 \) = 2
        \item \( C_1 \) = 2
        \item \( N_1 \) = 10
        \item \( M_1 \) = 6
        \columnbreak

        \item \( \lambda_{1_2} \) = 2
        \item \( \mu_2 \) = 2.5
        \item \( C_2 \) = 2
        \item \( N_2 \) = 10
        \item \( M_2 \) = 6
        \columnbreak

        \item \( \lambda_2 \) = 2
        \item \( R \) = 2
        \item \( \alpha \) = 0.5
    \end{itemize}
\end{multicols}

The set of possible actions to choose from for player 1 and player 2 is the
set of thresholds that the EDs can choose from: 
\begin{equation}
    T_1 = \{ 0, \ldots, N_1 \}, \quad T_2 = \{ 0, \ldots, N_2 \}
\end{equation}

For this example the only Nash equilibrium of the game is achieved when both 
players choose a threshold of \( T_1 = 10, T_2 = 10 \).
This means that the two players' best response to each other is to only block
ambulances when they are full.

Although the Nash equilibria is a great theoretical measure it sometimes may be
% TODO: great theoretical measure?
inconsistent with our intuitive notions about what should be the outcome of a 
game \cite{myerson1978refinements}.
Therefore it might not be the best way to describe human behaviour.
Since the work of Maynard Smith \cite{smith1986evolutionary} evolutionary game 
theory gives the tools for the emergence of stable behaviour.
One such model that allows for asymmetric payoffs, as is the case above, is 
replicator dynamics.
Stable outcomes of this algorithm will correspond to a subset of Nash
equilibria but more importantly, will give a model of emergent behaviour.

In order to analyse the strategies played by the two EDs, the learning algorithm
asymmetric replicator dynamics is used \cite{asymmetricreplicatordynamics}.
The two players are treated as two separate populations where each 
individual in the population is assigned a strategy. 
As the game progresses the proportion of each player playing each strategy 
changes based on their previous interactions.
The fitness of each each strategy is defined as:

\begin{equation}\label{eq:asymmetric_fitness}
    f_x = Ay, \quad f_y = x^T B
\end{equation}

Here, \(x \in \mathbb{R}^{m \times 1} \) and
\(y \in \mathbb{R}^{n \times 1}\) correspond to the proportion of individuals 
that play each strategy on the two populations.
Similarly, the average fitness of each strategy is defined as:
\begin{equation}
    \phi_x = f_x x^T, \quad \phi_y = f_y y
\end{equation}

The rate of change of strategy \( i \) of both types of individuals is captured 
by:
\begin{equation}
    \frac{dx}{dt}_i = x_i((f_x)_i - \phi_x), \quad \text{ for all }i
\end{equation}

\begin{equation}
    \frac{dy}{dt}_i = y_i((f_y)_i - \phi_y), \quad \text{ for all }i
\end{equation}
% TODO: Too much info?

The use of a learning algorithm allows to investigate, not only the outcome of 
the game, but also how that outcome is reached.
Consider figure \ref{fig:ard-by-itself}. 
By running asymmetric replicator dynamics on the system the behaviour that 
emerges can be observed.
It can be seen that for this particular set of parameters the strategies of 
the two hospitals converge over time. 
Both hospital 1 (row player) and hospital 2 (column player) seem to be playing 
the same strategy \(s_{10}\) which indicates that thresholds \(T_1 = 10\) and 
\(T_2 = 10\) are played.
What is more important in this example is how the two hospitals reached these
decisions which also highlights the importance of using a learning algorithm.
Hospital 2 is able to reach the decision in a short amount of time while 
hospital 1 takes longer and goes through numerous strategies to get there.

@@
